CS222 Project Proposal

### 2019-12-10 proposal/proposal.tex
update related work

% zxy
\section{Related Work}

@@

% Bibliography
% \bibliographystyle{acm}
% \bibliographystyle{unsrt}
\bibliography{../full_list.bib}

>>>>

% zxy
\section{Related Work}
\paragraph{\textbf{Ensemble method}} 
Ensemble method solves the learning problem by combining several learners.
A few researchers have addressed the issue of combining a set of simple classifier. 
Beriman\cite{BreimanBagging} proposed a method for generating multiple versions of a predictor by making bootstrap replicates of the learning set. 
However, this method actually increased the amount of computation since it trained the learned repeatedly.
Schapire\cite{Schapire1989The} proposed the boosting method to converting a weak learning algorithm into one that achieves arbitrarily high accuracy by combining a set of weak learners.
This method was developed by Freund et al.\cite{Freund1995A}, who proposed an adaptive version of the boost.
Subsequent weak learners are tweaked in favor of those instances misclassified by previous classifiers. 
Friedman et al.\cite{FriedmanGreedy} proposed a new method called gradient boosting. 
It performed additive optimization in functional space, which compensated for the weakness of weak classifiers in the light of the gradient of their loss function.

@@

% Bibliography
% \bibliographystyle{acm}
\bibliographystyle{unsrt}
\bibliography{../full_list.bib}
